Bird beak's elaboration and innovation

### 2023-06-08 Analysis/06-Figure_with_correlations.Rmd
Update 06-Figure_with_correlations.Rmd

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable_super_orders.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_super_orders, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Species projected onto\nthe whole phylogeny major axes") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_super_orders, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Species projected onto\ntheir superorders' major axes")
dev.off()

>>>>

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable_super_orders.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_super_orders, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "A") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_super_orders, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "B")
dev.off()
